\documentclass{cv}

\begin{document}

\centerline{
  \Large{
    \textbf{Dhanat Satta-awalo}
  }
}
\centerline{Bangkok, Thailand}
\centerline{Medical student · Software · Aviation · Machine learning}
\centerline{thewdhanat.com \textbullet{} thew@thewdhanat.com}

\section{Education}
\begin{cv_table}
  \cveduitem{Doctor of Medicine}{Faculty of Medicine, Chulalongkorn University}{2018--2024}
  \cveduitem{High school}{Triam Udom Suksa School}{2015--2018}
  \cveduitem{Middle school}{Saint Dominic School}{2012--2015}
\end{cv_table}

\section{Elective courses}
\begin{cv_table}
  \cvelecitem{Clinical Experience In Anesthesiology}{Faculty of Medicine, Chulalongkorn University}{2023}
  \cvelecitem{Introduction To Computation And Bioinformatics}{Faculty of Medicine, Chulalongkorn University}{2022}
  \cvelecitem{Introduction To Perioperative Medicine}{Faculty of Medicine, Chulalongkorn University}{2020}
  \cvelecitem{Biomedical Engineering For Medical Students}{Faculty of Engineering, Chulalongkorn University}{2020}
  \cvelecitem{Computer Security}{Faculty of Engineering, Chulalongkorn University}{2020}
  \cvelecitem{Intro To law}{Faculty of Law, Chulalongkorn University}{2018}
\end{cv_table}

\section{Experience}
\begin{cv_table}
  \cvitemwithsubtitle{Established Thew AI Special Interest Group (SIG)}
  {\begin{cv_itemize}
      \item A community on Discord for medical students at MDCU who have an interest in artificial intelligence (AI).
      \item Weekly to monthly online meetings for the sharing and discussion of AI-related news and information.
    \end{cv_itemize}
  }{}{2022--Present}
  \cvitemwithsubtitle{Owner of thewdhanat.com website}
  {\begin{cv_itemize}
      \item My personal website. I usually write a blog post about technology here.
      \item Created with an emphasis on accessibility and performance optimization.
      \item Built with 11ty, hosted on Vercel, and continuous delivery from GitHub Actions.
    \end{cv_itemize}
  }{}{2020--Present}
  \cvitemwithsubtitle{Created and maintained MDCU research club website}
  {\begin{cv_itemize}
      \item A website for MDCU Research Club. It contains research news, research talk and researcher database.
      \item Developed with a consideration for accessibility, data security, and performance optimization.
      \item Built with Next.js and Strapi, hosted on Vercel and DigitalOcean, and continuous delivery from GitHub Actions.
    \end{cv_itemize}
  }{}{2020--Present}
  \cvitemwithsubtitle{Data Privacy Director}
  {\begin{cv_itemize}
      \item Led the Data Privacy committee for the Student Union of the Faculty of Medicine, Chulalongkorn University.
      \item Ensured the confidentiality and security of personal information belonging to medical students at MDCU.
      \item Provided counsel and advocated for the student union on matters pertaining to data privacy.
    \end{cv_itemize}
  }{}{2022}
  \cvitemwithsubtitle{Presented Machine Learning Overview}
  {\begin{cv_itemize}
      \item Presented a talk on the overview of machine learning at an annual event organized by the IT department.
      \item The topics include supervised learning, unsupervised learning, and applications in medicine.
    \end{cv_itemize}
  }{}{2020}
  \cvitemwithsubtitle{Headed database of cremation ceremony for cadaver donors}
  {\begin{cv_itemize}
      \item A web-based user interface for viewing, entering and editing the data for each donor.
      \item Built with Vue and json-based database hosted on GitHub.
    \end{cv_itemize}
  }{}{2019--2020}
  \cvitemwithsubtitle{Leaded LINE chatbot for elderly project}
  {\begin{cv_itemize}
      \item A LINE chatbot that reminds elderly to take medications.
      \item First runner-up winner in the 3\textsuperscript{rd} medical student innovation exhibition.
      \item Poster presentation at Beijing University of Posts and Telecommunications.
      \item Built with Rasa, the popular open source framework for building conversational AI assistants.
    \end{cv_itemize}
  }{}{2018}
\end{cv_table}

\section{Awards and Honours}
\begin{cv_table}
  \cvitemwithsubtitle{Engineering Professional and Academic Aptitude Test (PAT 3)}
  {Score: 292/300 (1\textsuperscript{st} rank)}{NIETS}{2018}
  \cvitemwithsubtitle{Google Code-in 2016 Grand Prinze Winner}
  {A contest that introduced pre-university students (ages 13-17) to open source software development}{Google Open Source Programs Office}{2017}
\end{cv_table}

\section{Activities}
\begin{cv_table}
  \cvitemwithsubtitle{ACLS Demonstration}
  {BLS \& ALS workshop}{MDCU Open House 2023}{1--2 April 2023}
  \cvitemwithsubtitle{BLS Instructor}
  {CPR Workshop}{Chula 106th Anniversary Homecoming}{26 March 2023}
  \cvitemwithsubtitle{BLS Instructor}
  {CPR Workshop}{Augmented Reality Hololens for CPR press conference}{2 February 2023}
  \cvitemwithsubtitle{BLS Instructor}
  {CPR Workshop "Everyone Can Be A Hero"}{Anan day 2018}{14 July 2018}
\end{cv_table}

\section{Selected Projects}
\begin{cv_table}
  \cvitemwithsubtitle{auto-twitter-cover}
  {\begin{cv_itemize}
      \item A simple program to change Twitter profile cover every sunrise and sunset
      \item The image is automatically fetch from from Unsplash when sunrise and NASA when sunset.
      \item Written in Go programming language.
    \end{cv_itemize}
  }{}{2021--Present}
  \cvitemwithsubtitle{vercel-shorturl}
  {\begin{cv_itemize}
      \item A simple script to generate personal short URL service.
      \item Utilized Vercel Edge Middleware to optimize speed.
      \item Integrated Amplitude analytics.
    \end{cv_itemize}
  }{}{2020--Present}
  \cvitemwithsubtitle{airtable-smtp}
  {\begin{cv_itemize}
      \item A simple script that send emails with data from Airtable through SMTP protocol.
      \item Created from experience gained during maintaining database of cremation ceremony for cadaver donors.
      \item Built with Node.js.
    \end{cv_itemize}
  }{}{2022}
  \cvitemwithsubtitle{MDCU Open House 2020 registration system}
  {\begin{cv_itemize}
      \item An online registration portal for visitors of the MDCU Open House 2020 event.
      \item Designed and implemented with a focus on accessibility, security, and performance optimization.
      \item Built with React and Firebase.
    \end{cv_itemize}
  }{}{2020}
  \cvitemwithsubtitle{biggame75}
  {\begin{cv_itemize}
      \item A web-based graphical interface for game in MDCU freshy camp.
      \item Built with React and Firebase.
    \end{cv_itemize}
  }{}{2019}
\end{cv_table}

\section{Certifications}
\begin{cv_table}
  \cvonlinecourseitem{IRB members, Researchers, Faculty members}
  {CITI Program}{CITI Program}{2021}
  \cvonlinecourseitem{Generative Adversarial Networks (GANs)}
  {DeepLearning.AI}{Coursera}{2021}
  \cvonlinecourseitem{How to Manage a Remote Team}
  {GitLab}{Coursera}{2021}
  \cvonlinecourseitem{AI for Medicine}
  {DeepLearning.AI}{Coursera}{2021}
  \cvonlinecourseitem{COVID-19 Training for Healthcare Workers}
  {Stanford University}{Coursera}{2021}
  \cvonlinecourseitem{Software Engineer Deep Learning}
  {Workera}{Workera}{2020}
  \cvonlinecourseitem{Microsoft Azure Musketeers}
  {Microsoft}{Microsoft}{2019}
\end{cv_table}

\section{Memberships}
\begin{cv_table}
  Data Privacy committee, the Student Union of the Faculty of Medicine, Chulalongkorn University & & 2021--Present \\
  MDCU Research Club, the Student Union of the Faculty of Medicine, Chulalongkorn University & & 2020--Present \\
  IT Department, the Student Union of the Faculty of Medicine, Chulalongkorn University & & 2018--Present \\
\end{cv_table}

\end{document}
